Supplemental Information: Continuous developmental changes in word recognition support language learning across early childhood

### 2025-04-04 paper/supplemental_information.Rmd
editing dataset description

Figure \ref{fig:dataset} gives the age distribution for each separate dataset.

```{r dataset, fig.cap="\\label{fig:dataset} Age distribution for each dataset, using three-month bins.", fig.pos="h!"}
ggplot(d_sub, aes(x = age))+ 
  geom_histogram(binwidth = 3) + 
  facet_wrap(~dataset_name, scale = "free_y") +
  xlab("Age (months)") + 
  ylab("Number of participants")
```

Figure \ref{fig:longitudinal} shows the distribution of measurement intervals for longitudinal studies within the dataset.

```{r longitudinal, fig.cap="\\label{fig:longitudinal} Number of administrations for datasets with repeated measurements, plotted by dataset.", fig.pos="h!"}

>>>>

Figure \ref{fig:dataset} gives the age distribution of unique participants for each separate dataset at different ages. 
Note that for some datasets, there are multiple administrations (i.e., experimental test sessions) for each participant.

```{r dataset, fig.cap="\\label{fig:dataset} Age distribution for each dataset, using three-month bins.", fig.pos="h!"}

# summarize participants by age bin
d_sub_admin_by_age <- d_sub |>
  mutate(age_bin = age %/% 3 * 3+1.5) |>
  group_by(dataset_name, age_bin) |>
  summarise(
    n_subj = n_distinct(subject_id),
    n_administration = n_distinct(administration_id)) |>
  ungroup()

# ggplot(d_sub, aes(x = age))+ 
#   geom_histogram(binwidth=3) + 
#   facet_wrap(~dataset_name, scale = "free_y") +
#   xlab("Age (months)") + 
#   ylab("Number of administrations")+
#   theme(strip.text.x = element_text(size = 5))

# plot number of participants across age
ggplot(d_sub_admin_by_age, aes(x = age_bin,y=n_subj))+ 
  geom_bar(stat="identity",width=3) + 
  facet_wrap(~dataset_name, scale = "free_y") +
  xlab("Age (months)") + 
  ylab("Number of participants")+
  theme(strip.text.x = element_text(size = 5))

Figure \ref{fig:longitudinal_descriptives} shows the distribution of measurement intervals for longitudinal studies within the dataset.

```{r longitudinal_descriptives, fig.cap="\\label{fig:longitudinal_descriptives} Number of administrations for datasets with repeated measurements, plotted by dataset.", fig.pos="h!"}
